%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Kathryn D. Huff

\documentclass[margin,line]{resume}
\bibliographystyle{IEEEtranSNK}
\usepackage{bibentry}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
\urlstyle{same}
\usepackage{xspace}
%\textheight=10.75in
\newcommand{\Cyclus}{\textsc{Cyclus}\xspace}%


%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Gwendolyn J.Y. Chee}
\begin{resume}

    % Contact Information
    \section{\mysidestyle Contact\\Information}
   PhD Student  \hfill e-mail: gchee2@illinois.com \vspace{0mm}\\\vspace{0mm}%
        \textsl{University of Illinois at Urbana-Champaign}
        \hfill github: github.com/gwenchee           \vspace{0mm}\\\vspace{0mm}%
    \textsl{Nuclear, Plasma, and Radiological Engineering}
        \hfill linkedin: linkedin.com/in/gwenchee/    \vspace{0mm}
    %__________________________________________________________________________________________________________________
    % Resume Objective
    %\section{\mysidestyle Objective}
		%Seeking research and teaching opportunities in nuclear engineering and scientific computation.%
    %__________________________________________________________________________________________________________________
    % Research Interests
    \section{\mysidestyle Research\\Interests}
		Advanced nuclear reactors, multi-physics
                simulation, nuclear fuel cycle analysis,
                scientific computation, high performance computing
                %
    %__________________________________________________________________________________________________________________
    % Academic Appointments
    %		\vspace{-2mm}
    %\section{\mysidestyle Academic\\Appointments}
    %           \vspace{-2mm}\\\vspace{-3mm}%
    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle PhD}
    \textbf{University of Illinois at Urbana-Champaign}, \textsc{Nuclear Engineering}\hfill \textbf{ Jan 2020 - Dec 2022}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Thesis: Fluoride-Salt-Cooled High Temperature Reactor Generative
        Design Optimization with Evolutionary Algorithms
        \item Advisors:  Dr. Kathryn D. Huff and Dr. Madicken Munk
        \item Graduate Concentration in Computational Science and Engineering
    \end{list2}\vspace{-1.5mm}
    \section{\mysidestyle MS}
    \textbf{University of Illinois at Urbana-Champaign}, \textsc{Nuclear Engineering}\hfill \textbf{ Aug 2017 - Dec 2019}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Thesis: Sensitivity Analysis of Nuclear Fuel Cycle Transitions
        \item Advisor:  Dr. Kathryn D. Huff
    \end{list2}\vspace{-1.5mm}

    \section{\mysidestyle BASc}
    \textbf{Queen’s University at Kingston, Canada}, \textsc{Engineering Physics}\hfill\textbf{Sept 2013 -- May 2017}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Thesis: Designing a System to Gaseous Hydrogen Charge Zirconium Alloys
        \item Concentration in Material Science
    \end{list2}\vspace{-1.5mm}
    %__________________________________________________________________________________________________________________
    % Research Experience
    \section{\mysidestyle Research\\Experience}
    \textbf{University of Illinois at Urbana-Champaign}, Urbana, IL\hfill \textbf{Aug 2017 -- Dec 2022}\\
		\textsl{Graduate Research Assistant, Nuclear Plasma and Radiological Engineering}\\\vspace{-3.7mm}
                \begin{list2}
                        \item Leveraged artificial intelligence genetic algorithms to optimize fluoride salt-cooled 
                        reactor geometry using Python package DEAP, 
                        and open-source OpenMC and Moltres tools
                        \item Collaborated with 14 scientists to benchmark the Fluoride-salt High-temperature 
                        Reactor by modeling the design in OpenMC
                        \item Led analysis, code and test development of the "Demand-Driven \textsc{Cycamore} Archetypes" 
                        NEUP project to construct demand-driven deployment algorithms and time series models in 
                        Python and C++ open-source tools, d3ploy and \Cyclus
                \end{list2}\vspace{-1.5mm}

\textbf{Argonne National Laboratory}, Lemont, IL \hfill \textbf{June 2020 - Aug 2020}\\\vspace{-4mm}%
		\textsl{Research Aide, Advanced Nuclear Energy Systems Group}\\
                \begin{list2}
                        \item Implemented variable salt-feed functionality and tests in ANL's NQA-1 certified Reactor Fuel Management 
                        and Depletion Python tool, ADDER
                        \item Conducted a code verification of ADDER's MSR depletion capability against published results from SCALE 
                \end{list2}\vspace{-1.5mm}

    \textbf{Argonne National Laboratory}, Lemont, IL \hfill \textbf{May 2019 - Aug 2019}\\\vspace{-4mm}%
		\textsl{Research Aide, Reactor Physics and Fuel Cycle Analysis Group}\\
                \begin{list2}
                        \item Investigated fuel cycle sensitivity analysis and optimization methods for the Department of Energy's 
                        Nuclear Fuel Cycle Options Campaign by coupling ANL's fuel cycle simulator, Dymond, 
                        with Sandia National Lab's optimization and uncertainty quantification tool, Dakota, using Python
                \end{list2}\vspace{-1.5mm}

        \textbf{Queen’s University at Kingston, Canada}, Kingston, ON \hfill \textbf{Sept 2016 - May 2017}\\\vspace{-4mm}%
		\textsl{Research Assistant, Nuclear Materials Research Group}\\
                \begin{list2}
                        \item Designed a Sieverts Apparatus to gaseously charge hydrogen gas into zirconium alloys to 
                        mimic hydrogen embrittlement of zirconium alloys used in nuclear reactors.
                \end{list2}\vspace{-1.5mm}

        \textbf{National University of Singapore}, Singapore \hfill \textbf{May 2016 - Aug 2016}\\\vspace{-4mm}%
		\textsl{Research Assistant, Centre for Advanced 2D Materials}\\
                \begin{list2}
                        \item Developed a MATLAB script to study the effect of Berry Curvature on electrons in graphene and the 
                        effects of changing the geometry of graphene devices on their electric fields. 
                \end{list2}\vspace{-1.5mm}

        \textbf{Nanyang Technological University}, Singapore \hfill \textbf{May 2015 - Aug 2015}\\\vspace{-4mm}%
		\textsl{Research Assistant, Polymeric Biomaterials Group}\\
                \begin{list2}
                        \item Conducted experiments to characterize nanoparticle enhanced polymer materials  
                \end{list2}\vspace{-1.5mm}
%__________________________________________________________________________________________________________________
     % Industry Experience
    \section{\mysidestyle Industry\\Experience}
    \textbf{Meta}, Menlo Park, CA \hfill \textbf{May 2021 - Aug 2021}\\\vspace{-4mm}%
    \textsl{PhD Software Engineer Intern (ML Track), FB Creators Wellbeing Team}\\
    \begin{list2}
            \item Implemented a viewer-personalized ML model in Facebook's comment 
            ranking infrastructure resulting in 1\% increase in user-engagement
            \item Constructed an end-to-end ML pipeline: dataset generation
            with DataSwarm, Gradient-boosting decision tree classifier
            training with PyTorch, A/B testing with online performance
            monitoring, and backend infrastructure support with Hack
    \end{list2}\vspace{-1.5mm}
    %__________________________________________________________________________________________________________________
    % Honors and Awards
    \section{\mysidestyle Honors and\\Awards}
    Women in Nuclear Chapter Excellence Award \hfill \textbf{2019}\vspace{.5mm}\\%
    Queen's University Dean Scholar  \hfill \textbf{2014-2017}\vspace{.5mm}\\
    Queen's University Principal's Entrance Scholarship \hfill \textbf{2013}\hfill 

    %__________________________________________________________________________________________________________________

    \section{\mysidestyle Journal\\Publications}
    %\section{\mysidestyle Refereed\\Journal\\Publications} % also, vspace below
    \nobibliography{cv}
      \begin{bibenum} 

        \item \textbf{Chee, G.}, Agosta, R.E.F., Bae, J.W., Flanagan, R.R., Scopatz, A.M., 
        Huff, K.D. "\textbf{Demand Driven Deployment Capabilities in Cyclus, a Fuel Cycle Simulator}," 
        Nuclear Technology. \url{https://doi.org/10.1080/00295450.2020.1753444}, Jul 2020
        \item Bae, J.W., Rykhlevskii, A., \textbf{Chee, G.}, Huff, K.D. ``Deep 
        Learning Approach to Nuclear Fuel Transmutation in a Fuel Cycle 
        Simulator.'' \textbf{Annals of Nuclear Energy}, vol. 139. 
        \url{https://doi.org/10.1016/j.anucene.2019.107230}, May 2020.

      \end{bibenum}
      %\vspace{2mm} % add this back if you return to Refereed Journal..
      %\section{\mysidestyle Submitted}
      %\begin{bibenum}
      %  \item 
      %\end{bibenum}
    \section{\mysidestyle Refereed\\Conference\\Proceedings}
    \begin{bibenum}
        \item Petrovic, B., Ramey, K., Hill, I., Losa, E., Elsawi, M., Lu, C. Gonzalez, J., 
        Novog, D., \textbf{Chee, G.}, Huff, K., Margulis, M., Read, N., Shwageraus, E. ``Preliminary Results of the NEA FHR Benchmark Phase I-A AND I-B (Fuel Element 2-D Benchmark)''
         \textbf{ANS M\&C 2021 - The International Conference on Mathematics and Computational Methods Applied 
         to Nuclear Science and Engineering}, Raleign, NC. Oct 2021.
        \item Nelson, A.G., \textbf{Chee, G.}, M.G. Jarrett. ``Molten Salt Reactor Depletion Techniques in the ADDER Reactor 
        Depletion and Fuel Management Analysis Code''
         \textbf{ANS M\&C 2021 - The International Conference on Mathematics and Computational Methods Applied 
         to Nuclear Science and Engineering}, Raleign, NC. Oct 2021.
    \item \textbf{Chee, G.}, Bae, J.W., Flanagan, R.R., Agosta, R.E.F., 
        Huff, K.D. ``Demonstration of Demand-Driven Deployment Capabilities in Cyclus''
         \textbf{Global/TopFuel}, Seattle, WA. Sept 2019.
    \item Flanagan, R.R., \textbf{Chee, G.}, Bae, J.W., Agosta, R.E.F., 
    Huff, K.D. ``Methods for automated fuel cycle facility deployment''
     \textbf{Global/TopFuel}, Seattle, WA. Sept 2019.
     \item \textbf{Chee, G.}, Park, G. T., 
    Huff, K.D. ``Validation of Spent Nuclear Fuel Output byCyclus, a Fuel Cycle Simulator Code''
     \textbf{American Nuclear Society Winter Meeting}, Orlando, FL, November 2018
     \item \textbf{Chee, G.}, Bae, J.W., 
    Huff, K.D. ``Validation of Spent Nuclear Fuel Output byCyclus, a Fuel Cycle Simulator Code''
     \textbf{ American Nuclear Society National Student Conference}, Gainesville, FL, April 2018.
    \end{bibenum}
    %__________________________________________________________________________________________________________________
    % Submitted Journal Publications
    %		\vspace{-2mm}
    %\section{\mysidestyle Submitted\\Journal\\Publications}
    %            Submitted Journal Publications \vspace{-2mm}\\\vspace{-3mm}%
    %__________________________________________________________________________________________________________________
    % Conference Publications
    \section{\mysidestyle Refereed\\Conference\\Abstracts}
    \begin{bibenum} 
    \item \textbf{Chee, G.}, Huff, K.D. `` Simulation of Spent Nuclear Fuel loading into a Final Waste 
    Repository'', \textbf{WM Symposia}, Phoenix, AZ, April 2019.
    \end{bibenum}
    \vspace{0.5em}
    %__________________________________________________________________________________________________________________
    % Technical Reports
    \section{\mysidestyle Technical\\Reports}
    \begin{bibenum} 
        \item \textbf{Chee, G.J.}, Agosta, R.E.F., Huff, K., ``Transition Scenario Demonstrations of CYCAMORE Demand Driven Deployment Capabilities.'' 
        \textbf{Advanced Reactors and Fuel Cycles Report Series}, Nuclear Plasma and Radiological Engineering, University of Illinois.  Report 
        UIUC-ARFC-2018-03, 
        \url{http://arfc.github.io/papers/chee_transition_2019.pdf} 
        Sept.2019.  
      \item \textbf{Chee, G.J.}, Bae, J.W., Huff, K., ``Numerical Experiments 
              For Verifying Demand Driven Deployment Algorithms.'' 
              \textbf{Advanced Reactors and Fuel Cycles Report Series}, Nuclear Plasma and Radiological Engineering, University of Illinois.  Report 
              UIUC-ARFC-2018-01, 
              \url{http://arfc.github.io/papers/bae_numerical_2018.pdf} 
              Apr.2018.  
    \end{bibenum}
    %__________________________________________________________________________________________________________________
    % Other Publications
    \section{\mysidestyle Other\\Publications}
    \begin{bibenum}
        \item \textbf{Chee, G.J.Y.} Fluoride-Salt-Cooled High Temperature Reactor Generative
        Design Optimization with Evolutionary Algorithms.
        PhD Dissertation --Nuclear, Plasma, and Radiological Engineering.
        University of Illinois, Urbana-Champaign.  December 2022.
      \item \textbf{Chee, G.J.Y.} Sensitivity Analysis of Nuclear Fuel Cycle Transitions. 
        M.S. Thesis --Nuclear, Plasma, and Radiological Engineering.
        University of Illinois, Urbana-Champaign.  December 2019.
      \item \textbf{Chee, G.} ``Designing a System to Gaseously Hydrogen Charge Zirconium Alloys''
        Undergraduate Thesis. Queen's University at Kingston. May 2017.
    \end{bibenum}
    %__________________________________________________________________________________________________________________
    % Software Products
    \section{\mysidestyle Software\\Products}
    \begin{bibenum}
    \item \textbf{Chee, G.}, Bae, J.W., Flanagan, R.R., Agosta, R.E.F., Scopatz, A.M.,
    Huff, K.D. d3ploy v1.0.1. \textbf{zenodo}, Sept 2019. 
            \url{10.5281/zenodo.3464123}.
    \end{bibenum}

    \section{\mysidestyle Media\\Coverage}
    \begin{bibenum}
        \item Sopkin, J. ``NPRE Graduate Student Spotlight: Gwendolyn Chee'' \textbf{NPRE News}, Urbana, IL: Illinois Engineering, Oct 22, 2019.\url{https://npre.illinois.edu/news/34609}.
        \item Mumm, S. ``Great response for NPRE's "Ask Me Anything!"'' \textbf{NPRE News}, Urbana, IL: Illinois Engineering, Oct 17, 2019.\url{https://npre.illinois.edu/news/34590}.
	\end{bibenum}
    %__________________________________________________________________________________________________________________
    % Invited Talks
    %\section{\mysidestyle Invited\\Talks}
 
    %__________________________________________________________________________________________________________________
    % Teaching Experience
    \section{\mysidestyle Engineering\\Teaching}
    \textbf{University of Illinois at Urbana-Champaign}\\
    \textsc{Dept. of Nuclear, Plasma, and Radiological Engineering}\\ 
               \textsl{NPRE 412, Nuclear Power Economics and Fuel Management} \hfill \textbf{Spring 2020}\\
               Teaching Assistant, Marked Assignments and taught three 1-hour classes
               \vspace{2mm}\\
        \textbf{Queen's University at Kingston}\\
        \textsc{Dept. of Physics, Engineering Physics, and Astronomy}\\ 
                        \textsl{PHYS 104/106}, Fundamental Physics \hfill \textbf{Fall 2015 - Spring 2017}\\
                        Teaching Assistant, Conducted weekly office hours

    %__________________________________________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle Scientific\\Computing\\Skills}
                \textbf{Languages} \hfill Python, C++, bash, CUDA, XML\vspace{.5mm}\\%
                \textbf{Build Systems} \hfill make, CMake\vspace{.5mm}\\%
                \textbf{Databases} \hfill HDF5, SQL\vspace{.5mm}\\%
                \textbf{Test Frameworks} \hfill pytest, nose\vspace{.5mm}\\%
                \textbf{Version Control} \hfill git, svn\vspace{.5mm}\\%
                \textbf{Other Tools} \hfill MS Virtual Studio, Sphinx, RAI, \LaTeX, MatLab\vspace{.5mm}\\%
                \textbf{Nuclear Software} \hfill OpenMC, MCNP, MOOSE, Moltres, \textsc{Cyclus}, DYMOND
                \vspace{-0.3cm}
    %__________________________________________________________________________________________________________________
    % Professional, Student Organizations


    \section{\mysidestyle Editing and\\Reviewing}
    \textbf{Manuscript Referee}~\hfill\emph{International Journal of Energy Research}\\%
                            %\mbox{}~\hfill\emph{Progress in Nuclear Energy}\vspace{2mm}\\%
    %\textbf{Grant Proposal Referee} \hfill \emph{Dept. of Energy Nuclear Energy University Programs}\\%
    %                        \mbox{}~\hfill\emph{Alfred P. Sloan Foundation}\vspace{2mm}\\%
    %\textbf{Book Proposal Referee} \hfill\emph{O'Reilly Media}\\%
                            %\mbox{}\hfill\emph{Elsevier}\vspace{2mm}\\%
                            \vspace{-0.3cm}
    \section{\mysidestyle Professional\\Service}
                \textbf{Advisor}, Women in Nuclear (UIUC Chapter) \hfill \textbf{2020-2021}\vspace{.5mm}\\%
                \textbf{President}, Women in Nuclear (UIUC Chapter) \hfill \textbf{2019-2020}\vspace{.5mm}\\%
                \textbf{Professional Development Chair}, Women in Nuclear (UIUC Chapter) \hfill \textbf{2018-2019}\\%
                \vspace{-0.5cm}
                %__________________________________________________________________________________________________________________
    \section{\mysidestyle Departmental\\Service}
		\textbf{Graduate Student Advisory Committee} \hfill \textbf{2020-2022}\\%

\vspace{-0.3cm}
    %__________________________________________________________________________________________________________________
    % References

\section{\mysidestyle References}
\textsl{Available upon request}

%______________________________________________________________________________________________________________________


    %__________________________________________________________________________________________________________________
\end{resume}

\end{document}


%______________________________________________________________________________________________________________________
% EOF

